Improving content discovery through combining linked data and data mining techniques

### 2016-05-06 report/chapters/06-evaluation.tex
Better word counting

This is especially supported by
the large performance increase from having simply enriched the data.
Given the enrichment in a lot of cases just added more higher order
properties describing the semantic properties themselves (e.g.
\textttmd:item\_rdf:type\_rdf:List{} appeared in some cases, which
tells us only that the \texttt{md:item} property found takes
list objects as values), we can safely conclude much of the
``enrichment'' has not added information about the content, but
just increased the triple count enough to make the clustering more
effective.

>>>>

This is especially supported by
the large performance increase from having simply enriched the data.
Given the enrichment in a lot of cases just added more higher order
properties describing the semantic properties themselves (e.g.
\texttt{md:item\_rdf:type\_rdf:List} appeared in some cases, which
tells us only that the \texttt{md:item} property found takes
list objects as values), we can safely conclude much of the
``enrichment'' has not added information about the content, but
just increased the triple count enough to make the clustering more
effective.
